Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-10-03 SI.tex
Update main and SI
update until question 5

@@

\subsection{Density of States (DOS) plots for the materials studied}
\label{sec:DOS}

@@

\input{BS_figures}

>>>>

For bulk systems, the accuracy of optical properties calculated
generally ranks by PBE $<$ G\textsubscript{0}W\textsubscript{0} $<$
BSE. This is because the calculation of the frequency-dependent
optical properties of a material involves a summation over the valence
and conduction states. Thus, the accuracy of these states determines
the calculated optical properties. Within Kohn-Sham density functional
theory (KS-DFT), the many-body effects are given by the
exchange-correlation energy which is approximated by functionals based
on the homogenous electron gas. This generally leads to an
underestimation of the bandgap and results in the first optical peak
being lower in energy in comparison to experiment. To go beyond
KS-DFT, the G\textsubscript{0}W\textsubscript{0} approximation
replaces the exchange-correlation energy with the self-energy in a bid
to include many-body effects through the interacting Green's function,
$G$, and the screened Coulomb potential, $W$. This generally leads to
an overestimation of the first optical peak as electron-hole coupling
is not taken into account. This can be remedied by solving the
Bethe-Salpeter equation using the eigenvalues obtained from
G\textsubscript{0}W\textsubscript{0}
(G\textsubscript{0}W\textsubscript{0} + BSE) which generally gives
good agreement with experiment.

@@

\iffalse
\subsection{Density of States (DOS) plots for the materials studied}
\label{sec:DOS}

@@

\input{BS_figures}
\fi

### 2019-10-03 paper.tex
update until question 5

that the result is affected by the choice of \textbf{ab initio}

@@

and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$, as seen in
Supplementary Section \ref{SI-ssec:gw}. Despite the different levels
of techniques used (Perdew-Burke-Ernzerhof (PBE) exchange-correlation
functional \cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, HSE06 hybrid
functionals or G\textsubscript{0}W\textsubscript{0} method), the
magnitude of dielectric functions calculated universally decreases

@@

absorption and electron energy loss spectrum (EELS), suffers the same

@@

simple model system explains the origin of the discrepancy of dielectric constant values reported in previous literature~\cite{Li_2016}.

@@

We further examine the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
thickness of a 2D material proposed in
Eq. \ref{eq:2D-Moss-perp}. Here we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material, which is defined as the
longest distance along the z-direction between any two atom nuclei
plus their covalent radii:
%
%
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where $i$, $j$ are two atoms in the 2D material and $r_{\mathrm{cov}}^{i}$
is the covalent radius of atom $i$ (Figure \ref{fig-3}{\textbf d} inset). 
%
%
$\alpha_{\mathrm{2D}}^{\perp}/(4 \pi \varepsilon_{0})$ shows an
excellent linear correlation with $\delta_{\mathrm{cov}}$, with
$R^{2}=0.98$, and a slope very close to $1/4\pi$ (Figure
\ref{fig-3}{\textbf d}), which agrees well with Eq
\ref{eq:2D-Moss-perp}.  This result indicates that
$\alpha_{\mathrm{2D}}^{\perp}$ has a strong physical meaning through
the geometry of the layer.  Similar to the molecular polarizability
which characterizes the volume of the electron cloud of an isolated
molecule \cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also related to the
volume of the electron cloud per unit area (from its definition), and
is naturally proportional to the thickness of the 2D
material. Supplementary Section
\ref{SI-ssec:theory-1-perp-fundamental} shows an explanation of this
behavior from fundamental electrostatics. Indeed, the universal
scaling relation for $\alpha_{\mathrm{2D}}^{\perp}$ in Figure
\ref{fig-3}{\textbf d} indicates that the quantity
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, measurable via
electronic and optical approaches
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM,Pedersen_2016,Klein_2016,Roch_2018},
is in reality the (dielectric) characteristic thickness of a 2D
material, and can be used to resolve the long-existing controversy
about the experimental thickness of 2D materials, such as graphene
\cite{Shearer_2016}.
%
To rule out the possibility that our conclusion are limited by the
number of materials used at HSE06 level, we further validate
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using a different
database \cite{Haastrup_2018}, from which we extracted the dielectric
properties of over 230 compounds calculated at the PBE level, and
superimpose with our results in Figure \ref{fig-3}{\textbf c} and
\ref{fig-3}{\textbf d} (see details in Supplementary Section
\ref{SI-sec:gpaw-1}). Although the dielectric properties may be
overestimated at PBE level due to underestimation of the bandgap
compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
with the linear coefficient very close to the HSE06 results (see
details in Supplementary Section \ref{SI-sec:gpaw-2}).

We have also searched for additional relations between the 2D
polarizabilities with other physical quantities, including the
effective carrier mass, quantum capacitance (density of states) and
total atomic polarizabilities with no apparent correlations being
found (Supplementary Section \ref{SI-sec:gpaw-3}).  We found however that
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} have a natural
connection with the screening properties of the layer.
%
In merit of the unit analysis, $\alpha_{\mathrm{2D}}^{\parallel}$ and
$\alpha_{\mathrm{2D}}^{\perp}$ both have unit of
$4\pi\varepsilon_{0} \cdot$[Length]. In other words,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
represent in- and out-of-plane characteristic lengths,
respectively. It is well-known that the in-plane screened
electrostatic potential $V(r)$ from a point charge as a function of
distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulomb potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we have drawn a generalized picture of the
dielectric nature of 2D materials via the 2D polarizability: the
dielectric screening of a point charge sitting in the middle of a 2D
material can be viewed as an ellipsoid with the length of principle
axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively. This is analog to the polarizability ellipsoid picture
of molecules used in spectroscopy \cite{Banwell_1994} (see
Supplementary Figure \ref{SI-fig:ellipsoid}). The polarizability
ellipsoid for a 2D material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as can be seen from the group 6
TMDCs in Table \ref{tbl:radii}.  Moreover, $r_{0}^{\parallel}$ is
generally larger for a smaller bandgap semiconductor, which
qualitatively explains the inverse proportional relation between
$\alpha_{\mathrm{2D}}^{\parallel}$ and $E_{\mathrm{g}}$ seen in
Eq. \ref{eq:2D-Moss-para}.  This gives a geometrical interpretation of
the bandgap in terms of the screening radius of the layer.

@@

We next show that the underlying physical mechanism linking 
polarizability to bandgaps allows us to further bridge 
the dielectric properties between 2D materials and 
their 3D bulk counterparts in a remarkable way. 
%The dielectric constant $\varepsilon$, although not well-defined for
%a monolayer 2D material, becomes applicable when the 2D layers are
%stacked. 
%
%
%
In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\textbf a}) as:
%
%
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
%
%
Here we neglect the effect of the stacking order of the layers.  The
dielectric constant $\varepsilon$ although not well-defined for a
monolayer 2D material becomes applicable when the 2D layers are put
together.
%
We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(\textit{x}-axis) as shown in Figure \ref{fig-4}{\textbf b} and \ref{fig-4}{\textbf c}. 
Both HSE06 and PBE datasets give almost identical results.  
%
We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement with a linear
regression slope of 1.01 and $R^2$ of 0.97. Conversely,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to the interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
%With a better model describing
%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
%the degree of interlayer coupling, the dielectric transition from 2D
%to 3D would be smoothly described.

Finally, we show that a general picture of the dielectric properties in
any dimension can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangles) can be
clearly distinguished from the bulk layered materials (orange squares)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as the electrostatic
transparency phenomena\cite{Liluhua_2014,Tian_2016,Li_2018} and the large exciton
binding energies
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
index of corresponding 2D layer (see additional details in
Supplementary Section \ref{SI-sec:aniso}), which is the basis for the
separation of bulk and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase
diagram.  For comparison, we also superimpose the dielectric
anisotropy indices of common semiconducting materials in other
dimensions (details see Supplementary Section \ref{SI-sec:aniso}) on
the phase diagram in Figure \ref{fig:aniso}. Bulk covalent (3D,
e.g. Si, GaN) and 0D (fullerenes) semiconductors show isotropic
dielectric properties, scattered on the line $\eta=1$. On the other
hand, reduced dimensionality increases the dielectric anisotropy of
materials such as planar organic semiconductor (OSc, 1D-2D,
e.g. CuPc), carbon nanotube (CNT, 1D), linear OSc (0D-1D,
e.g. polyacene and polyacetylene). Interestingly, most of these
materials also scatter along the boundary line separating the bulk and
2D regimes, indicating the criteria distinguishing 2D (more
anisotropic) and bulk layered materials (more isotropic) from the
$\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
dimensions. From the phase diagram, we can see that 2D and bulk
layered materials (also including 2D van der Waals heterostructure
(vdWH) \cite{Novoselov_2016}), provides more flexibility in
controlling the dielectric and electronic properties, compared with
semiconductors in other dimensions.

@@

%\section{Conclusion}
%\label{sec:org5fd1f1a}
%\todo[inline]{To be changed later when everything fixed}

@@

Add Mounet paper \cite{Mounet_2018}

>>>>

that the result is affected by the choice of \textit{ab initio}

@@

and $\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$ using different levels
of techniques, including Perdew-Burke-Ernzerhof (PBE)
exchange-correlation functional
\cite{Perdew_1996,Ernzerhof_1999,Paier_2005}, many-body Green function
method (G\textsubscript{0}W\textsubscript{0})~\cite{Hedin_1965} and
Bethe-Salpethe equation (BSE)~\cite{Onida_2002}, with increasing
accuracy of calculated optical properties (PBE $<$
G\textsubscript{0}W\textsubscript{0} $<$ BSE) due to including of
many-body screening and excitonic effects (details see Supplementary
Section \ref{SI-ssec:gw}). Despite various levels of theory involved,
the magnitude of dielectric functions calculated universally decreases

@@

absorption and electron energy loss spectrum (EELS, equivalent to $1 / \mathrm{Im}(\varepsilon(\omega))$), suffers the same

@@

simple model system explains the origin of the discrepancy of
dielectric constant values reported in previous
literature~\cite{Li_2016}.

@@

We further examine the validity of Eq.~\ref{eq:2D-Moss-perp}, i.e.,
the relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the thickness
of a 2D material. To test if the quantity $\hat{\delta_{\mathrm{2D}}}$
is physical, we choose the ``covalent'' thickness
$\delta_{\mathrm{cov}}$ of a 2D material as a
comparison. $\delta_{\mathrm{cov}}$ is defined as the longest distance
along the \textit{z}-direction between any two atom nuclei plus their covalent
radii:
%
%
\begin{equation}
  \label{eq:cov-thick}
  \delta_{\mathrm{cov}} = \mathrm{max}(|z^{i} - z^{j}|
  + r^{i}_{\mathrm{cov}} + r^{j}_{\mathrm{cov}})
\end{equation}
where $i$, $j$ are atomic indices in the 2D material and
$r_{\mathrm{cov}}^{i}$ is the covalent radius of atom $i$ (Figure
\ref{fig-3}{\textbf d} inset). As shown in Figure~\ref{fig-3}{\textbf
  d}, $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ (or equivalently,
$\hat{\delta}_{\mathrm{2D}}$) is very close to $\delta_{\mathrm{cov}}$
with a good linear correlation of $R^{2}=0.98$. This result indicates
a strong relation between $\alpha_{\mathrm{2D}}^{\perp}$ and the
geometry of the 2D layer, which can be approximated by
$\delta_{\mathrm{cov}}$. Similar to the molecular polarizability which
characterizes the volume of the electron cloud of an isolated molecule
\cite{Israelachvili_2011},
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ is also naturally
related to the characteristic thickness of the electron cloud of 2D
material. Supplementary Section
\ref{SI-ssec:theory-1-perp-fundamental} shows an explanation of this
behavior from fundamental electrostatics and why
$\alpha_{\mathrm{2D}}^{\perp} / \varepsilon_{0}$ is close to
$\delta_{\mathrm{cov}}$. Our proposed definition of
$\hat{\delta_{\mathrm{2D}}}$ of a 2D material based on
Eq. \ref{eq:2D-Moss-perp} may have impact
on some long-existing controversies about the experimental thickness
of 2D materials~\cite{Shearer_2016}, through the
measurable quantity $\alpha_{\mathrm{2D}}^{\perp}$
\cite{Antoine_1999,Cherniavskaya_2003,Krauss_1999_EFM}.
% 
%

To rule out the possibility that our conclusion are limited by the
number of materials used at HSE06 level, we further validate
Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp} using two
different 2D material databases \cite{Haastrup_2018,Mounet_2018}, from
which we extracted the dielectric properties of over 300 compounds
calculated at the PBE level, and superimpose with our results in
Figure \ref{fig-3}{\textbf c} and \ref{fig-3}{\textbf d}. Although the
calculated dielectric properties may be different due to different
choice of functionals as well as underestimation of the bandgap
compared with the more accurate HSE06 functionals
\cite{Van_Dyck_2017}, similar linear trends can be observed for both
$\alpha^{\parallel}_{\mathrm{2D}}$ and $\alpha_{\mathrm{2D}}^{\perp}$
with the linear coefficient very close to the HSE06 results, which
further proves the validity of our proposed relations. We have also
searched for additional relations between the 2D polarizabilities with
other physical quantities, including the effective carrier mass,
quantum capacitance (density of states) and total atomic
polarizabilities with no apparent correlations being found
(Supplementary Section \ref{SI-sec:gpaw-3}).

\subsection{Application in multilayer and bulk systems}
\label{sec:apply-electr-polar}
The concept of electronic polarizability is not limited to monolayer
materials, and can be applied to multilayer and bulk systems as
well. For a 2D material stack composed of $N$ layers, we can define
the electronic polarizability $\alpha_{\mathrm{NL}}$ similar to
Eqs. \eqref{eq:alpha-para-def} and \eqref{eq:alpha-para-def}. Note
$\alpha_{\mathrm{NL}}(N=1)$ is equivalent to $\alpha_{\mathrm{2D}}$.
Figure \ref{fig-4}\textbf{a} and \ref{fig-4}\textbf{b} show
$\alpha_{\mathrm{NL}}^{\parallel}$ and $\alpha_{\mathrm{NL}}^{\perp}$
as functions of $N$ for the selected 2H TMDCs,
respectively. Interestingly, we find that in all cases,
$\alpha_{\mathrm{NL}}$ exhibits nearly ideal linear relation with
$\alpha_{\mathrm{2D}}$, such that
$\alpha_{\mathrm{NL}}^{\parallel}= N \alpha_{\mathrm{2D}}^{\parallel}$
and $\alpha_{\mathrm{NL}}^{\perp}= N
\alpha_{\mathrm{2D}}^{\perp}$. Due to the relatively small
electric applied (0.01 eV/\AA{}), the interlayer interactions within
the stack are negligible. Under such circumstances, $\alpha_{\mathrm{2D}}$ of individual layers is additive, which leads to the following general relation:
\begin{equation}
  \label{eq:alpha-nl}
  \alpha_{\mathrm{NL}}^{p} = \sum_{i=1}^{N} \alpha_{\mathrm{2D, i}}^{p},\quad p=\parallel\ \mathrm{or}\ \perp
\end{equation}
where $\alpha_{\mathrm{2D, i}}$ is the electronic polarizability of
layer $i$, and $p$ is the direction of polarization. This relation can
be further used to calculate screening inside 2D heterostructures
\cite{Kumar_2016_jpcc,Andersen_2015_dielec_vdWH}.
%
%
%

We further look into the bulk systems. In a bulk layered material stacked by layers with equilibrium
inter-layer distance $L_{\mathrm{Bulk}}$, we define the polarizability
of individual layer $\alpha_{\mathrm{2D}}(L=L_{\mathrm{Bulk}})$ as
$\alpha_{\mathrm{Bulk}}$. Inspired by Eqs. \ref{eq:alpha-para-def} and
\ref{eq:alpha-perp-def}, the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of the bulk layered material can
be reconstructed by $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ (Figure \ref{fig-4}{\textbf a}) as:
%
%
\begin{subequations}
\begin{align}
  \label{eq:3D-para}
  \varepsilon^{\parallel}_{\mathrm{Bulk}}
  &= 1 + \frac{\alpha_{\mathrm{Bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}
  \approx 1 + \frac{\alpha_{\mathrm{2D}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}} \\
  \label{eq:3D-perp}
  \varepsilon^{\perp}_{\mathrm{Bulk}}
  &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
  \approx \left(1 - \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{align}
\end{subequations}
%
%
Here we neglect the effect of the stacking order of the layers.  The
dielectric constant $\varepsilon$ although not well-defined for a
monolayer 2D material becomes applicable when the 2D layers are put
together.
%
We compare the values of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from DFT calculations (\textit{y}-axis)
with those predicted using Eqs \ref{eq:3D-para} and \ref{eq:3D-perp}
(\textit{x}-axis) as shown in Figure \ref{fig-4}{\textbf b} and \ref{fig-4}{\textbf c}. 
Both HSE06 and PBE datasets give almost identical results.  
%
We observe that
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ values calculated by DFT and
predicted by Eq. \ref{eq:3D-para} are in good agreement with a linear
regression slope of 1.01 and $R^2$ of 0.97. Conversely,
$\varepsilon_{\mathrm{bulk}}^{\perp}$ values predicted from
Eq. \ref{eq:3D-perp} agree well with the DFT-calculated values when
$E_{\mathrm{g}}>4$ eV, while the deviation becomes larger when
$E_{\mathrm{g}}$ reduces. The above results indicate that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to the interlayer coupling and overlap between induced
dipoles\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. 
%With a better model describing
%$\alpha_{\mathrm{bulk}}^{\perp}$ as function of $\alpha_{\mathrm{2D}}^{\perp}$ and
%the degree of interlayer coupling, the dielectric transition from 2D
%to 3D would be smoothly described.

\subsection{Unified geometric represenation of $\alpha_{\mathrm{2D}}$}
\label{sec:unif-geom-repr}

%
Lastly, we demonstrate that both $\alpha_{\mathrm{2D}}^{\parallel}$
and $\alpha_{\mathrm{2D}}^{\perp}$ can be unified using a geometric
picture. In merit of the unit analysis,
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
both have unit of $4\pi\varepsilon_{0} \cdot$[Length]. In other words,
they represent in- and out-of-plane characteristic lengths,
respectively. It is well-known that the in-plane screened
electrostatic potential (Keldysh potential) $V(r)$ from a point charge
as a function of distance $r$:
$V(r) = {\displaystyle \frac{e}{4 \alpha_{\mathrm{2D}}^{\parallel}}}
\left[H_{0}({\displaystyle \frac{2\varepsilon_{0}
      r}{\alpha_{\mathrm{2D}}^{\parallel}}}) - Y_{0}( {\displaystyle
    \frac{2
      \varepsilon_{0}r}{\alpha_{\mathrm{2D}}^{\parallel}}})\right]$
\cite{Keldysh_1979_eps_multi,Pulci_2014}, where $H_{0}$ is the Struve
function and $Y_{0}$ is the Bessel function of second kind, is
associated with the in-plane screening radius
$r_{0}^{\parallel}=\alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$, such that $V(r,r/r^{\parallel}_{0} \gg 1)$ reduces
to the simple Coulomb potential in vacuum. Combining with the result
that $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ characterizes the
thickness of a 2D material, we can view the dielectric screening of a
point charge sitting in the middle of a 2D material as an ellipsoid
with the radii of principle axes to be
$r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/(2
\varepsilon_{0})$ and
$r_{0}^{\perp} = \alpha^{\perp}_{\mathrm{2D}}/(2 \varepsilon_{0})$,
respectively, as illustrated in Figure~\ref{fig-ellip}\textbf{a}.
This is analog to the polarizability ellipsoid picture of molecules
used in spectroscopy \cite{Banwell_1994}. The polarizability ellipsoid
for a 2D material is in general ultra flat, with
$r_{0}^{\parallel} \gg r_{0}^{\perp}$, as demonstrated by the examples
of group 6 2H TMDCs (Figure~\ref{fig-ellip}\textbf{a} and
~\ref{fig-ellip}\textbf{b}). The polarizability ellipsoid picture
provides further insights into the physical nature of
$\alpha_{\mathrm{2D}}$: $r_{0}^{\parallel}$ is close to the exciton
radius that confined within the 2D plane~\cite{Pulci_2014}, which is
generally larger for a smaller bandgap semiconductor, and can be
converted through the exciton binding energy as proposed in
Refs. \citenum{Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}
Eq. \ref{eq:2D-Moss-para}. On the other hand, $r_{0}^{\perp}$ may be
indirectly deduced from Stark effect
\cite{Pedersen_2016,Klein_2016,Roch_2018}.
% and the low-frequency Raman
% scattering modes of 2D materials \cite{Tan_2012,Zhang_2013}.

@@

Inspired by the polarizability ellipsoid model, we show that a general picture of the dielectric properties in
any dimension can be drawn by studying the dielectric
anisotropy. We define the dielectric anisotropy index $\eta$ as:
\begin{equation}
  \label{eq:anisotropy}
  \begin{aligned}[t]
    \eta =
    \begin{cases}
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\varepsilon^{ii}}{\varepsilon^{jj}}\right)},
      \ \mathrm{Bulk\ Materials}\\
      {\displaystyle \min_{i \neq j}}
      {\displaystyle
        \left(\frac{\alpha_{\mathrm{2D}}^{ii}}{\alpha_{\mathrm{2D}}^{jj}}\right)},
      \ \mathrm{2D\ Materials}\\
    \end{cases}
  \end{aligned}
\end{equation}
$\eta=1$ indicates the material has isotropic dielectric properties
while $\eta \to 0$ means the dielectric property is highly
anisotropic. Figure \ref{fig:aniso} shows the phase diagram of $\eta$
as function of $E_{\mathrm{g}}$ for 2D materials and their bulk
counterparts. Interestingly, the 2D materials (blue triangles) can be
clearly distinguished from the bulk layered materials (orange squares)
with the boundary line determined to be
$\eta =0.048 (E_{\mathrm{g}}/ \mathrm{eV})+0.087$. The much lower
$\eta$ values for 2D materials compared with their bulk counterparts
indicates a high dielectric anisotropy, which is responsible for the
unique 2D optoelectronic properties, such as the electrostatic
transparency phenomena\cite{Liluhua_2014,Tian_2016,Li_2018} and the large exciton
binding energies
\cite{Pulci_2014,Tran_2014,Chernikov_2014_EB_MoS2_2D3D,Berkelbach_2013}. From
Eqs. \ref{eq:2D-Moss-para}, \ref{eq:2D-Moss-perp} and
\ref{eq:anisotropy} we can see $\eta$ is roughly proportional to
$\delta \cdot E_{\mathrm{g}}$, which explains the observation that
$\eta$ for 2D materials increase almost linearly with
$E_{\mathrm{g}}$, since the layer thickness $\delta$ (mostly 3--10
\AA{}) of the 2D materials investigated varies much less than
$E_{\mathrm{g}}$ (0.1--7 eV) (Figure \ref{fig-3}b and
\ref{fig-3}c). Further analysis shows that the dielectric anisotropy
index of any bulk layered material $\eta_{\mathrm{Bulk}}$ obeys
$\eta_{\mathrm{Bulk}} \geq {\displaystyle \frac{4
    \eta_{\mathrm{2D}}}{(\eta_{\mathrm{2D}}+1)^{2}}} \geq
\eta_{\mathrm{2D}}$, where $\eta_{\mathrm{2D}}$ is the anisotropy
index of corresponding 2D layer (see additional details in
Supplementary Section \ref{SI-sec:aniso}), which is the basis for the
separation of bulk and 2D regimes in the $\eta-E_{\mathrm{g}}$ phase
diagram.  For comparison, we also superimpose the dielectric
anisotropy indices of common semiconducting materials in other
dimensions (details see Supplementary Section \ref{SI-sec:aniso}) on
the phase diagram in Figure \ref{fig:aniso}. Bulk covalent (3D,
e.g. Si, GaN) and 0D (fullerenes) semiconductors show isotropic
dielectric properties, scattered on the line $\eta=1$. On the other
hand, reduced dimensionality increases the dielectric anisotropy of
materials such as planar organic semiconductor (OSc, 1D-2D,
e.g. CuPc), carbon nanotube (CNT, 1D), linear OSc (0D-1D,
e.g. polyacene and polyacetylene). Interestingly, most of these
materials also scatter along the boundary line separating the bulk and
2D regimes, indicating the criteria distinguishing 2D (more
anisotropic) and bulk layered materials (more isotropic) from the
$\eta-E_{\mathrm{g}}$ diagram, can also be applied to other
dimensions. From the phase diagram, we can see that 2D and bulk
layered materials (also including 2D van der Waals heterostructure
(vdWH) \cite{Novoselov_2016}), provides more flexibility in
controlling the dielectric and electronic properties, compared with
semiconductors in other dimensions.

@@

\section{Conclusion}
%\label{sec:org5fd1f1a}
%\todo[inline]{To be changed later when everything fixed}

@@
